\thetitle

### 2023-06-03 lang-design.tex
Fix typo.

Even though we cannot prove partial recursors are \textit{the
most powerful} reasoning tool for extensible inductive types,
the fact that propositional partial
recursors can derive injectivity already demonstrate itself as a good \textit{extensional characterization} of
(non-indexed) extensible inductive type (under certain
constraints)---because we can ``embed'' vanilla inductive types into
types supporting a partial recursor: a bit more formally speaking, and
restricting our focus to non-indexed inductive types:

>>>>

Even though we cannot prove partial recursors are \textit{the
most powerful} reasoning tool for extensible inductive types,
the fact that propositional partial
recursors can derive injectivity already demonstrates itself as a good \textit{extensional characterization} of
(non-indexed) extensible inductive type (under certain
constraints)---because we can ``embed'' vanilla inductive types into
types supporting a partial recursor: a bit more formally speaking, and
restricting our focus to non-indexed inductive types:
